% !TEX root = ../my-thesis.tex
%
%\selectlanguage{english}  
\chapter{Sinfonevada: Dataset of Floristic diversity in Sierra Nevada forest (SE Spain)}\label{sec:sinfonevada}

\mbox{}
\vfill
{\color{ctcolormain}\textbf{Antonio J. Pérez-Luque}}; Francisco J. Bonet-García; Ramón Pérez-Pérez; Rut Aspizua; Juan Lorite \& Regino Zamora. 2014. \emph{Phytokeys}, 35: 1-15. \href{https://doi.org/10.3897/phytokeys.35.6363}{doi:10.3897/phytokeys.35.6363}



\newpage

\paragraph{Abstract} \mbox{} \\
The Sinfonevada database is a forest inventory that contains information on the forest ecosystem in the Sierra Nevada mountains (SE Spain). The Sinfonevada dataset contains more than 7 500 occurrence records belonging to 270 taxa (24 of these threatened) from floristic inventories of the Sinfonevada Forest inventory. Expert field workers collected the information. The whole dataset underwent a quality control by botanists with broad expertise in Sierra Nevada flora. This floristic inventory was created to gather useful information for the proper management of \textit{Pinus} plantations in Sierra Nevada. This is the only dataset that shows a comprehensive view of the forest flora in Sierra Nevada. This is the reason why it is being used to assess the biodiversity in the very dense pine plantations on this massif. With this dataset, managers have improved their ability to decide where to apply forest treatments in order to avoid biodiversity loss. The dataset forms part of the Sierra Nevada Global Change Observatory (OBSNEV), a long-term research project designed to compile socio-ecological information on the major ecosystem types in order to identify the impacts of global change in this area.

\newpage

\paragraph{Resource Citation}
University of Granada-Andalusian Environmental Center (2013). Sinfonevada: Dataset of floristic diversity in Sierra Nevada forests (SE Spain), Spain. 7920 data records. Contributed by TRAGSA, University of Granada, OBS- NEV, Pérez-Luque AJ, Pérez-Pérez R, Bonet FJ, Aspizua R, Lorite J, Zamora R. Online at \href{http://www.gbif.es:8080/ipt/resource.do?r=sinfonevada}http://www.gbif.es:8080/ipt/resource.do?r=sinfonevada and \href{http://obsnev.es/noticia.html?id=5307}http://obsnev.es/noticia.html?id=5307, version 1.0 (last updated on 2013-08-01). Resource ID: GBIF Key: \href{http://www.gbif.org/dataset/db6cd9d7-7be5-4cd0-8b3c-fb6dd7446472}http://www.gbif.org/dataset/db6cd9d7-7be5-4cd0-8b3c-fb6dd7446472, Data Paper ID: doi: \href{10.3897/phytokeys.35.6363}10.3897/phytokeys.35.6363
